Insert the article title here

### 2020-07-23 tex/results.tex
rework sections
add context for rockstuhl work

\section{Rockstuhl replication}

@@

 \section{Ellis replication and validation}

>>>>

\subsection{Replication of results from Rockstuhl, et al., 2005}

%%% Rockstuhl work summary%%%%
The work of Rockstuhl et al. study the phonon-polariton response of silicon carbide (SiC)
nanoparticles using the boundary element method. They analyze different "cylindrical particles"
made of 6H-SiC as a function of geometrical cross section. These "cylinders" have an infinite
extension in the third dimension, and they solve these geometries numerically with a 2D 
boundary element method from their previous work \cite{rockstuhl2003}. 
%%% Rockstuhl work summary%%%%

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To complain with our quasistatic approach we chose the particular case where a=672 nm and 
b=328 nm.

\textbf{difference between methods, mesh and dielectric data}

\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
we will extend the third direction considerably, and study this effect.

\textit{mesh}: Their work does not provide any details regarding the discretization of their geometries or 
parameters involved in the simulations. We performed a grid independence study to make sure that we are
solving properly the physics and minimizing errors due to discretization.

\textit{dielectric data}: The use 6H-SiC as material, and they obtained their data from a a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications.

@@

 \subsection{Replication of results from Ellis et al., 2016, and validation}
